Macro Impacts

### 2016-08-24 Macro Impacts Revised.tex
conceptual points added

Consider the initial condition of a delta source along the z-axis in cylindrical coordinates:
\begin{align}
T(r,0) = \f{\abs{\frac{dE}{dx}}r_X}{\rho \sigma_X c_p}\delta(r),
\end{align}
Taking the Fourier transform of this initial condition over r and $\phi$ fixes $C_1$ as 
\begin{align}
C_1 =  2\pi \f{\abs{\frac{dE}{dx}}r_X}{\rho \sigma_X c_p}\int_{0}^{\infty}\delta(r)e^{i k r} dr = 2\pi\f{\abs{\frac{dE}{dx}}r_X}{\rho \sigma_X c_p}\,,
\end{align}
where the factor of $2 \pi$ comes from the $\phi$ integral.
$T$ in real space is given by inverting the Fourier transform:
\begin{align}
T(r,t) &=\frac{1}{\p{2\pi}} \int_0^\infty k_r \diff{k_r}\tilde{T} = \frac{2\pi}{2\pi}\f{\abs{\frac{dE}{dx}}r_X}{\rho \sigma_X c_p}\int_0^\infty k_r\diff k_r e^{-\alpha k_r^2 t}J_0(k_r r)\,,\\
&=\f{\abs{\frac{dE}{dx}}r_X}{2 \rho \sigma_X c_p \alpha t}\ e^{-\f{r^2}{4t\alpha}}\,.
\end{align}
Setting $T = T_\te{melt}$, we have
\begin{align}
r_\te{melt} = \sqrt{4t\alpha\ln\ps{\f{\abs{\frac{dE}{dx}}r_X}{2 \rho \sigma_X c_p \alpha T_\te{melt} t}}}\,.
\end{align}
where we've taken the positive branch of the square root, since we only care about the melt radius increasing. Then taking the derivative w.r.t to time gives
\begin{align}
\dot r_\te{melt} &=\sqrt{\f{\alpha}{t}}\f{\ln\p{\f{\abs{\frac{dE}{dx}}r_X}{2 \rho \sigma_X c_p \alpha T_\te{melt} t}} - 1}{\sqrt{\ln\p{\f{\abs{\frac{dE}{dx}} r_X}{2 \rho \sigma_X c_p \alpha T_\te{melt} t}}}}\,.
\end{align}
Since, for the parameters at hand, $\ln\p{\f{\abs{\frac{dE}{dx}}r_X}{2 \rho \sigma_X c_p \alpha T_\te{melt} t}}$ is at least of order 10 $>>$ 1, it is a reasonable approximation to take
\begin{align}
\dot r_\te{melt} &=\sqrt{\f{\alpha}{t}\ln\p{\frac{\abs{\frac{dE}{dx}}r_X}{2 \rho \sigma_X c_p \alpha T_\te{melt} t}}}\,.
\end{align}
Thus, the time at which the velocity of the melt front is that of the speed of sound, $v_p$, is given by using the Lambert W-function (or "ProductLog" in Mathamatica) as
\begin{align}
t_{\te{fast}} = \f{\alpha}{v_p^2}W\p{{\f{\abs{\frac{dE}{dx}}r_Xv_p^2}{2 \rho \sigma_X c_p \alpha^2 T_\te{melt}}}}
\end{align}
Plugging in $t_{\te{fast}}$ to $r_\te{melt}$, which is a solid approximation for the given case, gives
\begin{align}
r_\te{fast melt} =  \frac{2\alpha}{v_p}\sqrt{W\p{{\f{\abs{\frac{dE}{dx}}r_{X}v_p^2}{2 \rho \sigma_X c_p \alpha^2 T_\te{melt}}}}\ln\ps{\p{\frac{\abs{\frac{dE}{dx}}r_{X}v_p^2}{2 \rho \sigma_X c_p \alpha^2 T_\te{melt}}}\frac{1}{W\p{{\f{\abs{\frac{dE}{dx}}r_{X}v_p^2}{2 \rho \sigma_X c_p \alpha^2 T_\te{melt}}}}
}}}\,.
\end{align}
Notice that this has the form of $\sqrt{W(x)\ln\p{{\frac{x}{W(x)}}}}$, which gives $\sqrt{W(x)^2}$ by the identity $\ln\p{{\frac{x}{W(x)}}} = W(x)$ which holds when $x \geq -1/e$ which is true for the parameters at hand.  Thus, we have,
\begin{align}
r_\te{fast melt} =\frac{2\alpha}{v_p}W\p{{\f{\abs{\frac{dE}{dx}}r_{X}v_p^2}{2 \rho \sigma_X c_p \alpha^2 T_\te{melt}}}} = \frac{2\alpha}{v_p}W\p{\frac{r_{X}v_{X} v_p^2}{2 c_p \alpha^2 T_\te{melt}}}.
\end{align}
which is on the order of micrometers to tenths of micrometers for our case.

Conceptually, it would seem that $r_\te{fast melt}$ should be added to $r_\te{Macro}$ to give the full extent of material melted down.

>>>>

Consider the initial condition of a delta source along the z-axis in cylindrical coordinates:
\begin{align}
T(r,0) = \f{\abs{\frac{dE}{dx}}r_X}{\rho \sigma_X c_p}\delta(r),
\end{align}
Note that this model/initial condition is reasonable given that the delta source becomes a Gaussian with the same energy (assuming energy is conserved) an instant after the initial input of the delta source.

Taking the Fourier transform of this initial condition over r and $\phi$ fixes $C_1$ as 
\begin{align}
C_1 =  2\pi \f{\abs{\frac{dE}{dx}}r_X}{\rho \sigma_X c_p}\int_{0}^{\infty}\delta(r)e^{i k r} dr = 2\pi\f{\abs{\frac{dE}{dx}}r_X}{\rho \sigma_X c_p}\,,
\end{align}
where the factor of $2 \pi$ comes from the $\phi$ integral.
$T$ in real space is given by inverting the Fourier transform:
\begin{align}
T(r,t) &=\frac{1}{\p{2\pi}} \int_0^\infty k_r \diff{k_r}\tilde{T} = \frac{2\pi}{2\pi}\f{\abs{\frac{dE}{dx}}r_X}{\rho \sigma_X c_p}\int_0^\infty k_r\diff k_r e^{-\alpha k_r^2 t}J_0(k_r r)\,,\\
&=\f{\abs{\frac{dE}{dx}}r_X}{2 \rho \sigma_X c_p \alpha t}\ e^{-\f{r^2}{4t\alpha}}\,.
\end{align}
Setting $T = T_\te{melt}$, we have
\begin{align}
r_\te{melt} = \sqrt{4t\alpha\ln\ps{\f{\abs{\frac{dE}{dx}}r_X}{2 \rho \sigma_X c_p \alpha T_\te{melt} t}}}\,.
\end{align}
where we've taken the positive branch of the square root, since we only care about the melt radius increasing. Then taking the derivative w.r.t to time gives
\begin{align}
\dot r_\te{melt} &=\sqrt{\f{\alpha}{t}}\f{\ln\p{\f{\abs{\frac{dE}{dx}}r_X}{2 \rho \sigma_X c_p \alpha T_\te{melt} t}} - 1}{\sqrt{\ln\p{\f{\abs{\frac{dE}{dx}} r_X}{2 \rho \sigma_X c_p \alpha T_\te{melt} t}}}}\,.
\end{align}
Since, for the parameters at hand, $\ln\p{\f{\abs{\frac{dE}{dx}}r_X}{2 \rho \sigma_X c_p \alpha T_\te{melt} t}}$ is at least of order 10 $>>$ 1, it is a reasonable approximation to take
\begin{align}
\dot r_\te{melt} &=\sqrt{\f{\alpha}{t}\ln\p{\frac{\abs{\frac{dE}{dx}}r_X}{2 \rho \sigma_X c_p \alpha T_\te{melt} t}}}\,.
\end{align}
Thus, the time at which the velocity of the melt front is that of the speed of sound, $v_p$, is given by using the Lambert W-function (or "ProductLog" in Mathamatica) as
\begin{align}
t_{\te{fast}} = \f{\alpha}{v_p^2}W\p{{\f{\abs{\frac{dE}{dx}}r_Xv_p^2}{2 \rho \sigma_X c_p \alpha^2 T_\te{melt}}}}
\end{align}
Plugging in $t_{\te{fast}}$ to $r_\te{melt}$, which is a solid approximation for the given case, gives
\begin{align}
r_\te{fast melt} =  \frac{2\alpha}{v_p}\sqrt{W\p{{\f{\abs{\frac{dE}{dx}}r_{X}v_p^2}{2 \rho \sigma_X c_p \alpha^2 T_\te{melt}}}}\ln\ps{\p{\frac{\abs{\frac{dE}{dx}}r_{X}v_p^2}{2 \rho \sigma_X c_p \alpha^2 T_\te{melt}}}\frac{1}{W\p{{\f{\abs{\frac{dE}{dx}}r_{X}v_p^2}{2 \rho \sigma_X c_p \alpha^2 T_\te{melt}}}}
}}}\,.
\end{align}
Notice that this has the form of $\sqrt{W(x)\ln\p{{\frac{x}{W(x)}}}}$, which gives $\sqrt{W(x)^2}$ by the identity $\ln\p{{\frac{x}{W(x)}}} = W(x)$ which holds when $x \geq -1/e$ which is true for the parameters at hand.  Thus, we have,
\begin{align}
r_\te{fast melt} =\frac{2\alpha}{v_p}W\p{{\f{\abs{\frac{dE}{dx}}r_{X}v_p^2}{2 \rho \sigma_X c_p \alpha^2 T_\te{melt}}}} = \frac{2\alpha}{v_p}W\p{\frac{r_{X}v_{X} v_p^2}{2 c_p \alpha^2 T_\te{melt}}}.
\end{align}
which is on the order of micrometers to tenths of micrometers for most marco radii which, for $r_X > 10^-8$ results in $r_\te{fast melt} < r_X$ which is something of a problem.

This suggests that much of the melting occurs once the temperature field is expanding slower than the speed of sound, and that the expansion speed of the melt zone slows down very quickly.
